Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2024-12-18 main.tex

\begin{remark}\label{remark:improved_starreflection}
    The estimates in Proposition~\ref{proposition:starreflection} should be considered as \textit{proof-of-concept} but not as optimal in any sense.
    Some improvements are immediately possible if $\ell=n-1$. 
    Then the reflection $\Xi$ in Lemma~\ref{lemma:volumecomparison} satisfies the same properties as the mapping $\Xi_{1}$,
    mapping the simplex $T$ bijectively onto the $\Makoto$ and being the identity along the common face $S$.
    However, at any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of the Jacobian of $\Xi$ satisfy 
    %     \begin{gather*}
    %         \sigma_1      \leq \aspectratio(\calT) ( 1 + \diameterratio(\calT) ),
    %         \quad 
    %         \sigma_2,\dots,\sigma_{n-1} \leq 1,
    %         \quad 
    %         \sigma^{-1}_n \leq \aspectratio(\calT) ( 1 + \diameterratio(\calT) ),
    %         \\ 
    %         | \det\Jacobian\Xi^{  } |      \leq \aspectratio(\calT) \diameterratio(\calT),
    %         \quad 
    %         | \det\Jacobian\Xi^{-1} |      \leq \aspectratio(\calT) \diameterratio(\calT).
    %     \end{gather*}
    \begin{gather*} 
        | \det\Jacobian\Xi^{  } |      \leq \aspectratio(\calT) \diameterratio(\calT),
        \quad 
        | \det\Jacobian\Xi^{-1} |      \leq \aspectratio(\calT) \diameterratio(\calT),
        \\
        \sigma_{1}, \sigma_{n}^{-1}
        %&
        \leq 
        \frac{1}{2} 
        %\left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) + 1 \right)^{2} + \aspectratio(\calT)^{2} }
        +
        \frac{1}{2} 
        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) - 1 \right)^{2} + \aspectratio(\calT)^{2} }
        ,
        \\
        \sigma_2,\dots,\sigma_{n-1} \leq 1.
        %         \det(\Jacobian \Xi) &\leq \diameterratio(\calT) \aspectratio(T_2)
    \end{gather*}
    These estimates improve over the ones in Proposition~\ref{proposition:starreflection} when the reflection is over a single face.
    We believe that better estimates can be computed from the geometric data also in the other cases.
\end{remark}

@@

    Let $u \in W^{p}\Alt^{k}(\Omega)$ and write $g = \cartan u$. We define $g' = \Xi_{2}^{-\ast} \cartan u = \cartan \Xi_{2}^{-\ast} u$. 
    Then Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} give  
    \begin{align*}
        \| g' \|_{L^{p}(\Omega')}  
        \leq 
        \Cachttrafo{n}{k}{\ell_{M}}{p}(\calT)
        %\Cacht{n}{k}(\calT)
        %\Cachtprime{n}{k}(\calT)^{k} 
        %\Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
        \| g \|_{L^{p}(\Omega)}  
        .
    \end{align*}
    By induction assumption, there exists $w' \in W^{p}\Alt^{k}(\Omega')$ such that $\cartan w' = g'$.
%     We have 
%     \begin{align*}
%         \| w' \|_{L^{p}(\Omega')} 
%         \leq 
%         \left( 
%         \Cachttrafo{n}{k}{\ell_{M}}{p}(\calT)
%         \Csiebtrafo{n}{k}{\ell_{M}}{p}(\calT)
%         \right)^{M-1}
%         C_{{\PF},k,T_{0},p}
%         \| g' \|_{L^{p}(\Omega')}  
%     \end{align*}
    Finally, $w = \Xi_{2}^{\ast} w' \in W^{p}\Alt^{k}(\Omega)$ satisfies $\cartan w = g$.
    Moreover, Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} show 
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}  
        \leq 
        \Csiebtrafo{n}{k}{\ell_{M}}{p}(\calT)
        %\Csieb{n}{k}(\calT)
        %\Csiebprime{n}{k}(\calT)^{k-1} 
        %\Cdetacht{n}{k}(\calT)^{\frac 1 p} 
        \| w' \|_{L^{p}(\Omega')} 
    \end{align*}
    We use the induction assumption to complete the estimates in the induction step is complete. The desired result follows. 
\end{proof}

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:curl}
    Let $\calT$ be a shellable $n$-dimensional triangulation, 
    and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
    Assume that $T_0, T_1, \dots, T_M$ be a shelling of $\calT$ and that $\bfu \in \bfW^{p}(\Omega,\curl)$ for some $1 \leq p \leq \infty$.
    Let $0 \leq \ell_{m} < n$ be such that $T_{m}$ shares $n - \ell$ faces with the previous simplices.
    \begin{itemize}
        \item 
        There exists $\bfw \in \bfW^{p}(\Omega,\curl)$ with $\curl \bfw = \curl \bfu$
        and such that the following estimates hold:
        \begin{gather*}
            \| \bfw \|_{L^{p}(T_{0})} \leq C_{{\PF},1,T_{0},p} \| \curl \bfu \|_{L^{p}(T_{0})}
        \end{gather*}
        and for each $T_{m} \in \calT$, $1 \leq m \leq M$ we have the recursive estimate 
        \begin{align*}
            \| \bfw \|_{L^{p}(T_{m})}
            &
            \leq  
            C_{\PF,T_{m},\Gamma_{m},1,p}(\calT) 
            \left( 
                \| \curl u      \|_{L^{p}(T_{m})} 
                +
                \Cfivetrafo{n}{1}{\ell_{m}}{p}(\calT)
                \| \curl u \|_{L^{p}(\Makoto_{m-1})}
            \right)
            \\&\qquad
            + 
            \Cfivetrafo{n}{1}{\ell_{m}}{p}(\calT)
            \| \bfw \|_{L^{p}(\Makoto_{m-1})}
            .
        \end{align*}
        \item 
        There exists $\bfw \in \bfW^{p}(\Omega,\curl)$ with $\curl \bfw = \curl \bfu$ 
        such that 
        \begin{align*}
            \| \bfw \|_{L^{p}(T_{m})}
            \leq 
            \left( 
            \prod_{i=1}^{M}
            \Cachttrafo{n}{1}{\ell_{m}}{p}(\calT)
            \Csiebtrafo{n}{1}{\ell_{m}}{p}(\calT)
            \right)
            C_{{\PF},1,T_{0},p}
            \| \curl \bfu \|_{L^{p}(\Omega)}
            .
        \end{align*}
    \end{itemize}
\end{theorem}

>>>>

\begin{remark}\label{remark:improved_starreflection}
    The estimates in Proposition~\ref{proposition:starreflection} should be considered as \textit{proof-of-concept} but not as optimal in any sense.
    Some improvements are immediately possible if $\ell=n-1$. 
    Then the reflection $\Xi$ in Lemma~\ref{lemma:volumecomparison} satisfies the same properties as the mapping $\Xi_{1}$,
    mapping the simplex $T$ bijectively onto the $\Makoto$ and being the identity along the common face $S$.
    However, at any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of the Jacobian of $\Xi$ satisfy 
    %     \begin{gather*}
    %         \sigma_1      \leq \aspectratio(\calT) ( 1 + \diameterratio(\calT) ),
    %         \quad 
    %         \sigma_2,\dots,\sigma_{n-1} \leq 1,
    %         \quad 
    %         \sigma^{-1}_n \leq \aspectratio(\calT) ( 1 + \diameterratio(\calT) ),
    %         \\ 
    %         | \det\Jacobian\Xi^{  } |      \leq \aspectratio(\calT) \diameterratio(\calT),
    %         \quad 
    %         | \det\Jacobian\Xi^{-1} |      \leq \aspectratio(\calT) \diameterratio(\calT).
    %     \end{gather*}
    \begin{gather*} 
        | \det\Jacobian\Xi^{  } |      \leq \volumeratio(\calT),
        \\
        \sigma_{1}, \sigma_{n}^{-1}
        \leq 
        \frac{1}{2} 
        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) + 1 \right)^{2} + \aspectratio(\calT)^{2} }
        +
        \frac{1}{2} 
        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) - 1 \right)^{2} + \aspectratio(\calT)^{2} }
        ,
        \\
        \sigma_2,\dots,\sigma_{n-1},\sigma_{n} \leq 1.
    \end{gather*}
    In particular,
    \begin{align*}
        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{2} |^{-\frac 1 p}
        \leq 
        \left( 
            \frac{1}{2} 
            \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) + 1 \right)^{2} + \aspectratio(\calT)^{2} }
            +
            \frac{1}{2} 
            \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) - 1 \right)^{2} + \aspectratio(\calT)^{2} }
        \right)
        \volumeratio(\calT)^{\frac 1 p}
        .
    \end{align*}
    These estimates improve over the ones in Proposition~\ref{proposition:starreflection} when the reflection is over a single face.
    We believe that better estimates can be computed from the geometric data also in the other cases.
\end{remark}

@@

    Let $u \in W^{p}\Alt^{k}(\Omega)$ and write $g = \cartan u$. We define $g' = \Xi_{2}^{-\ast} \cartan u = \cartan \Xi_{2}^{-\ast} u$. 
    Then Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} give  
    \begin{align*}
        \| g' \|_{L^{p}(\Omega')}  
        \leq 
        \Cachttrafo{n}{k+1}{\ell_{M}}{p}(\calT)
        %\Cacht{n}{k}(\calT)
        %\Cachtprime{n}{k}(\calT)^{k} 
        %\Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
        \| g \|_{L^{p}(\Omega)}  
        .
    \end{align*}
    By induction assumption, there exists $w' \in W^{p}\Alt^{k}(\Omega')$ such that $\cartan w' = g'$.
%     We have 
%     \begin{align*}
%         \| w' \|_{L^{p}(\Omega')} 
%         \leq 
%         \left( 
%         \Cachttrafo{n}{k}{\ell_{M}}{p}(\calT)
%         \Csiebtrafo{n}{k}{\ell_{M}}{p}(\calT)
%         \right)^{M-1}
%         C_{{\PF},k,T_{0},p}
%         \| g' \|_{L^{p}(\Omega')}  
%     \end{align*}
    Finally, $w = \Xi_{2}^{\ast} w' \in W^{p}\Alt^{k}(\Omega)$ satisfies $\cartan w = g$.
    Moreover, Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} show 
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}  
        \leq 
        \Csiebtrafo{n}{k}{\ell_{M}}{p}(\calT)
        %\Csieb{n}{k}(\calT)
        %\Csiebprime{n}{k}(\calT)^{k-1} 
        %\Cdetacht{n}{k}(\calT)^{\frac 1 p} 
        \| w' \|_{L^{p}(\Omega')} 
    \end{align*}
    We use the induction assumption to complete the estimates in the induction step is complete. The desired result follows. 
\end{proof}

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:curl}
    Let $\calT$ be a shellable $n$-dimensional triangulation, 
    and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
    Assume that $T_0, T_1, \dots, T_M$ be a shelling of $\calT$ and that $\bfu \in \bfW^{p}(\Omega,\curl)$ for some $1 \leq p \leq \infty$.
    Let $0 \leq \ell_{m} < n$ be such that $T_{m}$ shares $n - \ell_{m}$ faces with the previous simplices.
    \begin{itemize}
        \item 
        There exists $\bfw \in \bfW^{p}(\Omega,\curl)$ with $\curl \bfw = \curl \bfu$
        and such that the following estimates hold:
        \begin{gather*}
            \| \bfw \|_{L^{p}(T_{0})} \leq C_{{\PF},1,T_{0},p} \| \curl \bfu \|_{L^{p}(T_{0})}
        \end{gather*}
        and for each $T_{m} \in \calT$, $1 \leq m \leq M$ we have the recursive estimate 
        \begin{align*}
            \| \bfw \|_{L^{p}(T_{m})}
            &
            \leq  
            C_{\PF,T_{m},\Gamma_{m},1,p}(\calT) 
            \left( 
                \| \curl \bfu      \|_{L^{p}(T_{m})} 
                +
                \Cfivetrafo{n}{1}{\ell_{m}}{p}(\calT)
                \| \curl \bfu \|_{L^{p}(\Makoto_{m-1})}
            \right)
            \\&\qquad
            + 
            \Cfivetrafo{n}{1}{\ell_{m}}{p}(\calT)
            \| \bfw \|_{L^{p}(\Makoto_{m-1})}
            .
        \end{align*}
        \item 
        There exists $\bfw \in \bfW^{p}(\Omega,\curl)$ with $\curl \bfw = \curl \bfu$ 
        such that 
        \begin{align*}
            \| \bfw \|_{L^{p}(T_{m})}
            \leq 
            \left( 
            \prod_{i=1}^{M}
            \Cachttrafo{n}{2}{\ell_{m}}{p}(\calT)
            \Csiebtrafo{n}{1}{\ell_{m}}{p}(\calT)
            \right)
            C_{{\PF},1,T_{0},p}
            \| \curl \bfu \|_{L^{p}(\Omega)}
            .
        \end{align*}
    \end{itemize}
\end{theorem}
